Demonstration of matching route networks

### 2024-01-27 demo.qmd
Add rsgeo benchmark

@@

>>>>

```{r}
plot(rnet_y["value"], lwd = 5)
```

@@

# With rsgeo

```{r}
remotes::install_github("josiahparry/rsgeo", ref = "rent")

rnet_x = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_x_ed.geojson") |> 
  sf::st_transform(27700)
rnet_y = sf::read_sf("https://github.com/ropensci/stplanr/releases/download/v1.0.2/rnet_y_ed.geojson") |> 
  sf::st_transform(27700)

plot(rnet_x)
library(rsgeo)

x <- as_rsgeo(rnet_x)
y <- as_rsgeo(rnet_y)

# 3rd arg is distance 4th is slope tolerance
# distance is in units of the input data
system.time({
res <- rsgeo:::rnet_merge(x, y, 20, 0.2)

excluded <- setdiff(1:length(x), res$from)

from <- rnet_x[res$from,]
to <- lapply(res$to, \(.i) rnet_y[.i,])
to_mean_value <- sapply(res$to, \(.i) mean(rnet_y$value[.i]))

rnet_matched_rsgeo = dplyr::bind_cols(from, value = to_mean_value)
})

plot(rnet_matched_rsgeo["value"], lwd = 3)

```{r}
#| eval: false
#| echo: false
# to be joined on
plot(x[res$from], lwd = 2)
# joined onto x from y
plot(y[unique(unlist(res$to))], col = "red", lty = 3, add = TRUE, lwd = 2)
# not used
plot(x[excluded], col = "blue", lty = 3, add = TRUE)
```

Let's try matching the data:

```{r}
